%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cybersecurity Engineer - (PostGraduate)} % Rôle global
    {Capgemini} % Entreprise
    {Bordeaux - France} % Lieu
    {Nov. 2024 - Present} % Date globale
    {
      \begin{cvitems}
      \item {\textbf{Schneider Electric R\&D - DevOps} \hfill {\entrydatestyle{June 2025 – Present}}}
          \begin{itemize}[label=\tiny$\circ$, leftmargin=1.5ex]
            \item {Deployed and managed self-hosted GitHub runners across a hybrid infrastructure (On-premises \& Azure), optimizing build performance and security for development teams.}
            \item {Automated server provisioning and configuration using Ansible, standardizing environments and reducing manual setup time.}
            \item {Engineered CI pipelines using Github Actions.}
            \item {Developed Python automation scripts to eliminate repetitive administrative tasks.}
            \item {Modernized build systems by migrating legacy projects to CMake and Conan, improving dependency management and compilation speed.}
            \item {Provided Level 2/3 technical support to engineering teams.}
          \end{itemize}
      \end{cvitems}
    }

  \vspace{0.5em} % ou 1em pour plus d'espace
  \cventry
    {Cybersecurity Engineer - (PreGraduate)} % Rôle global
    {Capgemini} % Entreprise
    {Bordeaux - France} % Lieu
    {Oct. 2022 - Nov. 2024} % Date globale
    {
      \begin{cvitems}
      \item {\textbf{Capgemini - SOC Analyst} \hfill {\entrydatestyle{Jan. 2024 – Apr. 2025}}}
          \begin{itemize}[label=\tiny$\circ$, leftmargin=1.5ex]
            \item {Triaged and investigated security incidents across EDR, XDR and SIEM platforms.}
            \item {Executed end-to-end incident response (Containment, Eradication, Recovery).}
            \item {Engineered and fine-tuned detection rules to reduce false positives, signicantly improving the efficiency of the monitoring infrastructure.}
            \item {Wrote comprehensive forensic reports for client cybersecurity teams, translating technical logs into actionable remediation steps.}
            \item {On call-duty a week per month. Mentored junior analysts on investigation methodologies.}
          \end{itemize}
        \vspace{0.5em}
      \item {\textbf{BNP Paribas - SecOps Analyst} \hfill {\entrydatestyle{June 2023 - Dec. 2023}}}
          \begin{itemize}[label=\tiny$\circ$, leftmargin=1.5ex]
            \item {Member of the Operational Security Team.}
            \item {Access rights management.}
            \item {VoIP Project Management.}
            \item {Processing DLP alerts from L1 to L2.}
          \end{itemize}
        \vspace{0.5em}
      \item {\textbf{ADBM - Integration of a secure Information System} \hfill {\entrydatestyle{Jan. 2023 – May 2023}}}
          \begin{itemize}[label=\tiny$\circ$, leftmargin=1.5ex]
            \item {Study and Integration of a secure administration workstation.}
            \item {Hardening Debian and Redhat workstations.}
           \item {Deployment of various servers using Ansible playbooks (RedHat IDM, Satellite, SMTP Postfix with IMAP overlay, SFTP, Nextcloud).}
          \end{itemize}
      \end{cvitems}
    }

  \vspace{0.5em} % ou 1em pour plus d'espace
  \cventry
    {Armies Ministry}
    {Internship French Army Ministry}
    {Paris - France}
    {Sept. 2021 - Apr. 2022}
    {
      \begin{cvitems}
        \setlength\itemindent{1em}
        \item {Integration of a data diode within an information system.}
        \item {Unilateral data transmission.}
        \item {Proof of concept of data diode integration with associated issues (data integrity and data loss).}
        \item {Realization of tests and performance study.}
      \end{cvitems}
  }

\end{cventries}
